Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
remove old comments
wording

The public API is oriented towards batch processing. While classification and
regression algorithms can indeed make predictions for single samples, most \sklearn
objects are however intended to be used on batches of data. For efficiency reasons,
this indeed makes the use of NumPy and SciPy optimal by preventing the overhead
inherent to Python function calls and per-element dynamic type checking.
% Gilles: I don't think it is worth elaborating too much (if at all) on online learning. They are exceptions in scikit-learn.

@@

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
% XXX: Gael: I think that we should break the following lines in 2: the
% 'return self' hidden in the call to fit can be confusing to the casual
% reader
\begin{verbatim}
    from sklearn.linear_model import LogisticRegression
    clf = LogisticRegression(penalty="l1")
    clf.fit(X_train, y_train)
\end{verbatim}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"}, hence enabling
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C}, which
defines the strength of the regularization) are not explicitly defined and are
thus set to the default values. Upon calling \texttt{fit}, the model is then
learned from the training arrays \texttt{X\_train} and \texttt{y\_train}. Since
all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor. For example, to build a Random Forest on
the same training data, one would simply have to replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by \\
\texttt{RandomForestClassifier()}.

>>>>

The public API is oriented towards batch processing rather than online
processing. While classification and regression algorithms can indeed make
predictions for single samples, most \sklearn objects are however intended to be
used on batches of data. For efficiency reasons, this makes the use of NumPy and
SciPy optimal by preventing the overhead inherent to Python function calls or
due to per-element dynamic type checking.
% Gilles: I don't think it is worth elaborating too much (if at all) on online learning. They are exceptions in scikit-learn.

@@

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
\begin{verbatim}
    from sklearn.linear_model import LogisticRegression
    clf = LogisticRegression(penalty="l1")
    clf.fit(X_train, y_train)
\end{verbatim}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"}, hence enabling
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C}, which
defines the strength of the regularization) are not explicitly defined and are
thus set to the default values. Upon calling \texttt{fit}, the model is then
learned from the training arrays \texttt{X\_train} and \texttt{y\_train}. Since
all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor. For example, to build a Random Forest on
the same training data, one would simply have to replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by \\
\texttt{RandomForestClassifier()}.
